Replication of Gantman et al. 2024

### 2024-03-20 manuscript.qmd
begin work on phase 2 data collection integration

behavioral_data <- read_csv('data/final/behavioral.csv')
```

@@

eeg_data <- read_csv("data/final/eeg.csv", col_types = "cdcllcdc") %>%
  filter(!subject %in% excluded_subjects)
```

>>>>

behavioral_data <- read_csv('data/phase_2/final/behavioral.csv')
```

@@

eeg_data <- read_csv("data/phase_2/final/eeg.csv", col_types = "cdcllcdc") %>%
  filter(!subject %in% excluded_subjects)
```
